---
title: "sc_pipeline"
output: html_document
date: "2023-09-06"
---

<style type="text/css">
    body{
        font-size: 15px;
        line-height: 22px;
    }
    h1.title {
        font-size: 38px;
    }
    h1 {
        font-size: 28px;
        margin-top: 23px;
    }
    h2 {
        font-size: 24px;
        margin-top: 25px;
    }
    h3 {
      font-size: 20px;
        margin-top: 25px;
    }
    code.r{
        font-size: 13px;
    }
    pre {
        font-size: 14px;
    }
    p {
        margin-top:10px;
        margin-bottom:10px;
    }
    table {
        width: 60%;
        border-collapse: collapse;
        font-family: Futura, Arial, sans-serif;
    }
    th,td {
        padding: 5px;
    }
    th,td {
        border-bottom: 1px solid #ddd;
        border-top: 1px solid #ddd;
        padding-right: 20px
    }
</style>

```{r setup, include=FALSE}
options(knitr.table.format = "html") 
options(scipen=10)
knitr::opts_chunk$set(echo = TRUE, fig.path = output.dir)
knitr::opts_knit$set(root.dir = output.dir)
```

# HemaScopeR scRNA-seq data
--------------------------------

```{r Input_single, child=system.file('rmd', 'sc_step1_single.Rmd', package = 'HemaScopeR'), eval=(length(input.data.dirs) == 1)&Step1_Input_Data}
```

```{r Input_multi, child=system.file('rmd', 'sc_step1_multi.Rmd', package = 'HemaScopeR'), eval=(length(input.data.dirs) > 1)&Step1_Input_Data}
```

```{r QC_multi, child=system.file('rmd', 'sc_step2_multi.Rmd', package = 'HemaScopeR'), eval=(length(input.data.dirs) > 1)&Step2_Quality_Control}
```

```{r QC_single, child=system.file('rmd', 'sc_step2_single.Rmd', package = 'HemaScopeR'), eval=(length(input.data.dirs) == 1)&Step2_Quality_Control}
```

```{r Clustering, child=system.file('rmd', 'sc_step3.Rmd', package = 'HemaScopeR'), eval=Step3_Clustering}
```

```{r CellType, child=system.file('rmd', 'sc_step4.Rmd', package = 'HemaScopeR'), eval=Step4_Identify_Cell_Types}
```

```{r Visualization, child=system.file('rmd', 'sc_step5.Rmd', package = 'HemaScopeR'), eval=Step5_Visualization}
```

```{r DEGs, child=system.file('rmd', 'sc_step6.Rmd', package = 'HemaScopeR'), eval=Step6_Find_DEGs}
```

```{r CellCycle, child=system.file('rmd', 'sc_step7.Rmd', package = 'HemaScopeR'), eval=Step7_Assign_Cell_Cycle}
```

```{r Heterogeneity, child=system.file('rmd', 'sc_step8.Rmd', package = 'HemaScopeR'), eval=Step8_Calculate_Heterogeneity}
```

```{r MarkerGenes, child=system.file('rmd', 'sc_step9.Rmd', package = 'HemaScopeR'), eval=Step9_Violin_Plot_for_Marker_Genes}
```

```{r Lineage, child=system.file('rmd', 'sc_step10.Rmd', package = 'HemaScopeR'), eval=Step10_Calculate_Lineage_Scores}
```

```{r GSVA, child=system.file('rmd', 'sc_step11.Rmd', package = 'HemaScopeR'), eval=Step11_GSVA }
```

```{r Trajectory, child=system.file('rmd', 'sc_step12.Rmd', package = 'HemaScopeR'), eval=Step12_Construct_Trajectories}
```

```{r TF, child=system.file('rmd', 'sc_step13.Rmd', package = 'HemaScopeR'), eval=Step13_TF_Analysis}
```

```{r Interaction, child=system.file('rmd', 'sc_step14.Rmd', package = 'HemaScopeR'), eval=Step14_Cell_Cell_Interaction}
```

## Outputs

The outputs includes:

1. **Html report** :
[SC_base.html](./sc_base.html).
2. **Markdown report** :
[SC_base.md](./sc_base.md).
3. **Files** :
[`r project.names`](../).
