---
title: "st_pipeline"
output: html_document
date: "2023-09-06"
---

<style type="text/css">
    body{
        font-size: 15px;
        line-height: 22px;
    }
    h1.title {
        font-size: 38px;
    }
    h1 {
        font-size: 28px;
        margin-top: 23px;
    }
    h2 {
        font-size: 24px;
        margin-top: 25px;
    }
    h3 {
      font-size: 20px;
        margin-top: 25px;
    }
    code.r{
        font-size: 13px;
    }
    pre {
        font-size: 14px;
    }
    p {
        margin-top:10px;
        margin-bottom:10px;
    }
    table {
        width: 60%;
        border-collapse: collapse;
        font-family: Futura, Arial, sans-serif;
    }
    th,td {
        padding: 5px;
    }
    th,td {
        border-bottom: 1px solid #ddd;
        border-top: 1px solid #ddd;
        padding-right: 20px
    }
</style>

```{r setup, include=FALSE}
options(knitr.table.format = "html") 
options(scipen=10)
knitr::opts_chunk$set(echo = TRUE, fig.path = output.dir)
knitr::opts_knit$set(root.dir = output.dir)
```

# `r sampleName`
--------------------------------

```{r Input, child=system.file('rmd', 'st_step1.Rmd', package = 'HemaScopeR'), eval=TRUE}
```

```{r QC, child=system.file('rmd', 'st_step2.Rmd', package = 'HemaScopeR'), eval=Step2_QC}
```

```{r Clustering, child=system.file('rmd', 'st_step3.Rmd', package = 'HemaScopeR'), eval=Step3_Clustering}
```

```{r DEGs, child=system.file('rmd', 'st_step4.Rmd', package = 'HemaScopeR'), eval=Step4_Find_DEGs}
```

```{r SVF, child=system.file('rmd', 'st_step5.Rmd', package = 'HemaScopeR'), eval=Step5_SVFs}
```

```{r Interaction, child=system.file('rmd', 'st_step6.Rmd', package = 'HemaScopeR'), eval=Step6_Interaction}
```

```{r CNV, child=system.file('rmd', 'st_step7.Rmd', package = 'HemaScopeR'), eval=Step7_CNV}
```

```{r Deconvolution, child=system.file('rmd', 'st_step8.Rmd', package = 'HemaScopeR'), eval=Step8_Deconvolution}
```

```{r CellCycle, child=system.file('rmd', 'st_step9.Rmd', package = 'HemaScopeR'), eval=Step9_Cellcycle}
```

## Outputs

The outputs includes:

1. **Html report** :
[ST_base.html](./st_base.html).
2. **Markdown report** :
[ST_base.md](./st_base.md).
3. **Files** :
[`r sampleName`](../).
4. **Final data**:
[st_object.rds](./st_object.rds),
[st_object.h5ad](./st_object.h5ad)
